---
title: "Gun Control Chi-Square"
author: "Priscilla Hare"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I am Priscilla and I am updating this markdown file here. 


```{r}

library(tidyverse)

gc_df <- read_csv("gc_df.csv")

```

We are asking: Is there a significant difference in recommended gun control action for male and female respondents (should guns be easier, harder, or same diffuclty to get)?

adding more text

tyoing something...

this is top secret

Priscilla: data wrangling and counts
```{r}

get_guns <- gc_df %>% 
  filter(gender != "NA", 
         make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% #count function can give you counts for categorical data
  spread(make_get_guns, n) %>% #puts the df into a contingency table format
  select(-gender)

rownames(get_guns) <- c("Female", "Male")


```

My name is Anna the collaborator and I'm going to be doing chi-square test for independence!

We ask: "Is there a significant difference association between sex and opinion on whether guns should be more difficult, easier, or the same difficulty to get?"

```{r}
# Let's look at the actual proportions:

guns_prop <- prop.table(as.matrix(get_guns), 1)
guns_prop

# Run chi-square test for independence
guns_x2 <- chisq.test(get_guns)
guns_x2

```

"Recommended government action on gun access differed significantly between male (n = ) and female (n = ) respondents ($\chi^2$(`r guns_x2$parameter`) =..., p < 0.001). Notably , a much higher proportion of female respondents (57.4%) recommend making it more difficult to get guns, compare to 40.4% for male respondents"






